Models

### 2021-10-14 analysis/05_model_metrics.Rmd
Save out table for manuscript
exclude some columns from estimates table

>>>>

Write out table of model estimates for manuscript
```{r}
metric_model_table %>% 
  filter(model_id == "base", metric %in% c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")) %>% 
  select(-c(model, model_id, warning, formula, statistic, df)) %>% 
  write_csv(here::here("figures", "man_model_table.csv"))
```
